\section*{Getting around in Milan}
\label{getting-around}
\pagestyle{cropmarksstyle}
Azienda Trasporti Milanesi (ATM) operates a public transport network in Milan. Single tickets cost
€~1.50 and are available from newsstands, tobacconists (tabaccherie), bars and automatic ticket
machines in metro stations. 24\,h (€~4.50) and 48\,h (€~8.25) tickets, as well as a \emph{carnet} of 10 single
trips (€~13.80) are also available. An evening ticket (€~3.00) allows unlimited travel after 20:00.

Tickets should be stamped at the start of every journey and every time you change vehicles. To stamp
your ticket insert it into the slot in the electronic ticket machine on board overground vehicles or
at the ticket barriers in the metro. It is then valid for 90 minutes unlimited use (bus or tram), or
the completion of your full metro journey. Tickets are not sold on board and you will not find a
self-service ticket machine at bus and tram stop.

\section*{Code of Conduct}
\label{coc}
The OpenStreetMap Foundation is dedicated to providing a harassment-free conference experience for everyone, regardless of gender, gender identity and expression, sexual orientation, disability, physical appearance, body size, race, age or religion. We do not tolerate harassment of conference participants in any form. Sexual language and imagery is not appropriate for any conference venue, including talks.

Conference participants violating these rules may be sanctioned or expelled from the conference without a refund at the discretion of the conference organizers.

Our anti-harassment policy can be found at 2018.stateofthemap.org/codeofconduct
