\newpage
\enlargethispage{1\baselineskip}
\section*{Welcome to Milan and State of the Map 2018} \label{welcome}
This booklet provides you essential information
about the conference, the location and the schedule.  We are proud of the participation of the
OpenStreetMap community and our rich program but there is even more!  Please do get involved and
take advantage of the off-schedule sessions, discussions and spaces.

\paragraph*{Help desk} \label{welcome-helpdesk}
You already know the registration desk, located on the ground floor (Building 3, same as the whole
conference). It is also your port of call if you need support or help. We are listening to every
question, report and comment related to the event, the code of conduct (page~\pageref{coc}) or any
aspect of the organisation.

\paragraph*{Programme}
You can find the diverse programme on page~\pageref{saturday}ff. Full abstracts of all talks are available at https://2018.stateofthe\\map.org/program

\paragraph*{More than just talks} \label{welcome-location}
Room S.1.6 is available during the whole conference as free and open space offering chairs and tables
to talk to each other, work on your projects or just relax. Rooms S.1.3 (Saturday and Monday only) and S.1.4 are available for
self-organised sessions.  Please come to the welcome desk next to De Donato hall to announce your session.

\paragraph*{Sponsors} \label{welcome-sponsors}
We would like to thank our sponsors for making this event possible and for their support to the
OpenStreetMap Foundation.
\newpage
